Model Finding for Recursive Functions in SMT\thanks{ This research is partially supported by the Inria technological development action ``Contre-exemples Utilisables par Isabelle et Coq'' (CUIC). }

### 2015-05-07 tex/main.tex
more

The translation alters $\varphi$ in two main ways. First, it restricts the
quantification on function definitions for $\con{f}$ to the corresponding
uninterpreted type $\fargtype{\con{f}}$ and inserts appropriate selectors
$\fargx{\con{f}}{i}$. Second, it augments $\varphi$ with additional existential
constraints
$\exists a : \fargtype{\con{f}}.\;\, (\vecfarg{\con{f}}( a ) \teq \vec t)$; these
ensure that the restricted definition for $\con{f}$ covers all relevant tuples
of terms, namely the ones for which an $\con{f}$ application exists and is
relevant to the satisfiability of $\varphi$.
%\jb{what does ``current branch of'' mean? can we drop it / rephrase it / vague
%it up?}

If $t$ is an application of a logical predicate $\boolop
\in \{{\neg}, {\wedge}, {\vee}, {\teq}, {\lite}\}$,
$\conv_0$ calls itself recursively on the arguments $t_i$ and polarity $\pol(
\boolop, i, p )$, where $\pol$ is defined as
\begin{equation*}
\pol( \boolop, i, p ) =
\begin{cases}
p & \text{if either $\boolop \in \{{\wedge}, {\vee}\}$ or $\boolop = \lite$ and $i \in \{2, 3\}$} \\[-\jot]
\pnegate p & \text{if $\boolop = {\neg}$} \\[-\jot]
\pnone & \text{otherwise}
\end{cases}
\end{equation*}
The negation $\pnegate p$ of a polarity $p$ is $\pneg$ if $p$ is $\ppos$, $\ppos$
if $p$ is $\pneg$, and $\pnone$ if $p$ is $\pnone$.

>>>>

The translation alters $\varphi$ in two main ways. First, it restricts the
quantification on function definitions for $\con{f}$ to the corresponding
uninterpreted type $\fargtype{\con{f}}$ and inserts appropriate selectors
$\fargx{\con{f}}{i}$. Second, it augments $\varphi$ with additional existential
constraints
$\exists a : \fargtype{\con{f}}.\;\, \vecfarg{\con{f}}( a ) \teq \vec t$; these
ensure that the restricted definition for $\con{f}$ covers all relevant tuples
of terms, namely the ones for which an $\con{f}$ application exists and is
relevant to the satisfiability of $\varphi$.
%\jb{what does ``current branch of'' mean? can we drop it / rephrase it / vague
%it up?}

If $t$ is an application of a predicate $\boolop$,
%\in \{{\neg}, {\wedge}, {\vee}, {\teq}, {\lite}\}$,
$\conv_0$ calls itself recursively on the arguments $t_i$ and polarity $\pol(
\boolop, i, p )$, where $\pol$ is defined as
\begin{equation*}
\pol( \boolop, i, p ) =
\begin{cases}
p & \text{if either $\boolop \in \{{\wedge}, {\vee}\}$ or $\boolop = \lite$ and $i \in \{2, 3\}$} \\[-\jot]
\pnegate p & \text{if $\boolop = {\neg}$} \\[-\jot]
\pnone & \text{otherwise}
\end{cases}
\end{equation*}
The negation $\pnegate p$ of a polarity $p$ is $\pneg$ if $p$ is $\ppos$, $\ppos$
if $p$ is $\pneg$, and $\pnone$ if $p$ is $\pnone$.
